---
title: "Reality-Wren"
author: "Greg Shriver"
date: "2023-11-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction

This document is part instruction manual and part data summary tool focused on the collection, wranggling, and summarizing passive audio recordings (PAR) data.  Data are generated by automated recording units (ARUs) deployed along an urban rural gradient from Newark, DE to Landenberg, PA.

### Carolina Wren Vocalization types

We selected four Carolina Wren song vocalizations to train the BirdNET model and screen the XX months of recordings. Carolina Wrens vocalization types used in this analysis include;

#### Male Song

insert sonogram

#### Female Chatter

insert sonogram

#### Raspy

insert sonogram

#### TaDit

insert sonogram


### Table 1. Study site ID, Lat, Long, # hours recorded 




You can embed an R code chunk like this:

```{r fig.height=5}

lat <- c('36.07, 36.08, 38.89, 37.56')
lon <- c('72.44, 73.45, 72.01, 70.22')
df <- data.frame(lat, lon)
summary(df)


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
